\documentclass{resume}
\usepackage[left=0.2in,top=0.15in,right=0.2in,bottom=0.15in]{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\setstretch{0.55}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{\normalsize Harsh Saw}
\address{\footnotesize +1 (778) 583-2260 \\ Kelowna, BC, Canada}
\address{\footnotesize
  \href{mailto:mister.harshkumar@gmail.com}{mister.harshkumar@gmail.com} \\
  \href{https://www.linkedin.com/in/harsh-kumar-s-32727b247/}{LinkedIn} \\
  \href{https://github.com/Harshksaw}{GitHub} \\
  \href{https://harshsaw.me/}{harshsaw.me}
}
\begin{document}

\vspace{-.5em}
\begin{rSection}{Summary}
{\scriptsize Full-stack software engineer with 2+ years of internship experience shipping production systems across distributed messaging, cloud infrastructure, and AI pipelines. Currently building RAG and agentic workflows at OmMuse; prior work spans real-time marketing platforms, video streaming infrastructure, and mobile apps serving thousands of users.}
\end{rSection}\vspace{-0.6em}


\begin{rSection}{Education}
{\scriptsize \textbf{Bachelor of Computer Information Systems}, Okanagan College \hfill Expected Dec 2026}
\end{rSection}\vspace{-0.5em}


%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\scriptsize \textbf{Software Engineer Intern} \hfill Nov 2025 -- Present\\
\textbf{\href{https://ommuse.com/}{OmMuse} (Seattle)}
\begin{itemize}\itemsep -4pt
    \item Architecting \textbf{AI-powered semantic search} and natural language chat for enterprise studio workflows using a \textbf{RAG} pipeline (\textbf{MongoDB Vector Store, AWS Bedrock}), enabling producers to query projects, tracks, and collaborators conversationally.
    \item Built \textbf{HubSpot CRM} sync for a 12K+ user music platform in \textbf{Go} --- async batch worker using \textbf{sync.Map} deduplication (30s flush, 100-user chunks) syncing live metrics across 8 API trigger points; platform manages 18K+ tracks and 67\,GB of user audio.
    \item Engineered a cross-platform desktop uploader (\textbf{Electron}) with persistent folder-sync engine (\textbf{chokidar + SQLite WAL}), parallelized \textbf{S3 multipart uploads}, \textbf{OAuth 2.0 PKCE} auth flow, and a typed IPC bridge exposing 70+ \textbf{gRPC} service methods to the renderer.
    \item Shipped features across a polyglot monorepo (\textbf{Go gRPC/protobuf}, TypeScript/React, Python) unified by \textbf{Bazel}, owning full deployment infrastructure --- \textbf{AWS} (S3, SQS, ECR), \textbf{Docker}, \textbf{Pulumi} IaC, Envoy proxy, and \textbf{GitHub Actions} CI/CD.
\end{itemize}

\scriptsize \textbf{Full-Stack Developer Intern} \hfill Jun 2025 -- Sept 2025\\
  \textbf{\href{https://morethinks.com/}{MoreThinks Solutions Ltd.}, Burnaby, BC}
  \begin{itemize}\itemsep -4pt
    \item Developed full-stack features using \textbf{Qwik.js} and \textbf{SurrealDB} in a monorepo, with CI/CD automation via \textbf{AWS EKS and API Gateway}.
    \item Engineered automated token generation and \textbf{vector embedding pipelines}, producing structured data consumed by ML services for recommendation.
  \end{itemize}

\scriptsize \textbf{Software Engineer Intern} \hfill Dec 2024 -- Jun 2025\\
\textbf{\href{https://bwishernepal.com/}{Bwisher Ltd}, Remote}
\begin{itemize}\itemsep -4pt
    \item Architected a multi-channel marketing platform using \textbf{Apache Kafka} and \textbf{BullMQ}, orchestrating personalized SMS, email, and \textbf{WhatsApp} campaigns with custom offers across \textbf{30K+ users} while feeding real-time CRM and analytics pipelines.
    \item Designed idempotent \textbf{NestJS} and \textbf{FastAPI} microservices for payment and credit workflows with retry and exponential backoff strategies, eliminating duplicate transactions in high-stakes financial operations.
    \item Owned end-to-end deployment infrastructure with \textbf{Jenkins, Kubernetes, Prometheus,} and \textbf{Grafana}; shipped features behind feature flags enabling safe tenant-by-tenant rollouts with instant kill-switch control.
    \item Built \textbf{FastAPI} services for customer behavior aggregation and demand forecasting, generating segmented targeting data consumed by the \textbf{Kafka}-driven campaign pipeline to optimize offer personalization across 30K+ users.
\end{itemize}

\scriptsize \textbf{Full-Stack Developer Intern} \hfill Jan 2024 -- Dec 2024\\
\textbf{\href{https://jythu.com/}{Jythu Ltd}, Remote}
\begin{itemize}\itemsep -4pt
    \item Shipped two production \textbf{React Native} apps (LMS + admin panel) with \textbf{Node.js} backends serving \textbf{2K+ learners}; provisioned full \textbf{AWS} infrastructure with \textbf{Terraform} and \textbf{GitHub Actions} CI/CD, with multi-layer anti-piracy controls including device-bound auth.
    \item Built an end-to-end video streaming pipeline using \textbf{FFmpeg} HLS transcoding delivered via \textbf{S3/CloudFront}, orchestrated through \textbf{SQS, Lambda, and SNS} --- reducing seek time from \textbf{30s to 1.5s} and cutting bandwidth by \textbf{{\raise.17ex\hbox{$\scriptstyle\sim$}}70\%}.
\end{itemize}

\end{rSection}\vspace{-0.7em}


%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\scriptsize \textbf{Document Intelligence Platform (RAG)}
{\scriptsize \textit{FastAPI, LangChain, Qdrant, Groq, Google Gemini, AWS ECS Fargate, Docker}}
\hfill
\href{https://aidoc.harshsaw.ca/}{Live Demo} |
\href{https://github.com/Harshksaw/document_portal}{GitHub}

\begin{itemize}\itemsep -4pt
  \item \textbf{Architected} a multi-tenant RAG platform with session-isolated \textbf{Qdrant} indexes, enabling semantic search and conversational Q\&A over PDF, DOCX, and TXT documents.
  \item \textbf{Engineered} resilient LLM orchestration using \textbf{LangChain RunnableWithFallbacks}, implementing automatic provider failover (Groq $\rightarrow$ Gemini) with streaming retrieval pipelines featuring context-aware query rewriting and hybrid document chunking.
  \item \textbf{Deployed} to \textbf{AWS ECS Fargate} with GitHub Actions CI/CD and multi-worker Uvicorn scaling; designed idempotent ingestion using \textbf{SHA-256} fingerprinting to deduplicate embeddings and reduce redundant indexing.
\end{itemize}

\scriptsize \textbf{CodeExpo -- Browser-Based IDE \& Sandbox Environment}
{\scriptsize \textit{React, Node.js, WebSocket, Docker, Nginx, Zustand, xterm.js}}
\hfill
\href{https://code.harshsaw.ca}{Live Demo}\,\textbullet\,
\href{https://github.com/Harshksaw/Project-IDX-Codesandbox}{GitHub}
\begin{itemize}\itemsep -4pt
    \item Engineered a full-stack browser-based IDE replicating a local dev environment --- live terminal via \textbf{xterm.js} and \textbf{WebSocket}, real-time code execution with browser preview pane, and \textbf{Socket.IO} file synchronization across the workspace.
    \item Architected containerized sandbox environments using \textbf{Docker} with multi-stage builds and \textbf{Nginx} reverse proxy, managing isolated execution contexts and environment lifecycle per session.
    \item Delivered a native-feeling developer workspace with a split-pane layout (editor, terminal, live preview) powered by \textbf{Monaco Editor}; managed synchronized file tree and tab state via Zustand with \textbf{React Query} handling optimistic updates for a lag-free editing experience.
\end{itemize}

\end{rSection}\vspace{-0.7em}


\begin{rSection}{Technical Skills}
\scriptsize
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1.5ex}} l }
Languages             & JavaScript (ES6+), TypeScript, Python, Go (Golang), Bash \\
Frontend \& Mobile    & React, Next.js, React Native, Qwik.js, Electron \\
Backend \& Messaging  & NestJS, FastAPI, Express, Fastify, GraphQL, gRPC/Protobuf, Apache Kafka, BullMQ, RabbitMQ \\
Databases             & PostgreSQL, MongoDB, DynamoDB, Redis, MySQL, SurrealDB, SQLite \\
Cloud \& DevOps       & AWS, Azure, Docker, Kubernetes, Terraform, Pulumi, Bazel, Jenkins, GitHub Actions \\
AI \& GenAI           & LangChain, LangSmith, AutoGen, RAG, FAISS, Pinecone, Qdrant, AstraDB, AWS Bedrock \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}
\scriptsize
\begin{itemize}\itemsep -7pt
    \item Built an end-to-end stock prediction pipeline covering \textbf{500 S\&P 500 constituents} over 5 years of 15-minute bar data --- \textbf{XGBoost} models trained across 26 intraday horizons on \textbf{4$\times$ NVIDIA H100 GPUs} (DRAC), with automated warm-start retraining every 15 minutes during market hours, served via a \textbf{FastAPI} backend backed by a \textbf{PostgreSQL} data warehouse and a multi-rolling feature pipeline.
    \item Ranked in the \textbf{top 2\% of verified freelancers} on \href{https://www.freelancer.com/u/misterharshkumar}{Freelancer.com} with a 5-star rating, delivering 25+ production-grade projects.
    \item Won an inter-university college hackathon, demonstrating innovative problem-solving and technical proficiency.
\end{itemize}
\end{rSection}

\end{document}
